---
title: "Assignment 04"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
```



Complete a hypothesis test on the `InsectSprays` data (`dat` below)

```{r}
data("InsectSprays")
dat = InsectSprays %>%
  rename(insects = count) %>%
  filter(spray == 'A' | spray == 'B')
dat
```

Begin your hypothesis test here. You can do it with both the analytical approach (`t.test`)  and the permutation test technique.
```{r}
tmp <- dat %>%
  group_by(spray) %>%
  summarize(mean_insects = mean(insects))

A <- tmp %>% filter(spray == 'A')
B <- tmp %>% filter(spray == 'B')

mean_diff_assumption = A$mean_insects - B$mean_insects
mean_diff_assumption
```


```{r}
pool_of_insects = dat %>% select(insects) %>% pull()
mean_diffs = c()

for(i in 1:10000) {
  pool_indicies = sample(length(insects))
  spray_a = mean(pool_of_insects[pool_indicies[1:12]])
  spray_b = mean(pool_of_insects[pool_indicies[13:14]])
  mean_diff = spray_a - spray_b
  mean_diffs[i] = mean_diff 
}

insect_final = tibble(mean_diff = mean_diffs)

std_dev = sd(mean_diffs)
total_mean_diff = mean(mean_diffs)


insect_final %>%
  ggplot(aes(x=mean_diff)) +
  geom_histogram(bins = 30) +
  geom_vline(xintercept = mean_diff_assumption, col = 'red') +
  geom_vline(xintercept = total_mean_diff - 2*std_dev , col = 'blue') +
  geom_vline(xintercept = total_mean_diff + 2*std_dev , col = 'blue')
  
# Inside 95% range...inconclusive ... NULL HYPOTHESIS
```


```{r}

```





## Explore the Data - Wine Data
Data from kaggle.com <https://www.kaggle.com/zynicide/wine-reviews>


#### Assignment  

If you were head of purchasing for a liquor store, what would you choose to buy and why?

```{r, message = FALSE, warning = FALSE}
dat = read_csv('https://foco-ds-portal-files.s3.amazonaws.com/winemag-data-130k-v2.csv')
head(dat)
```


Show summary statistics (note anything interesting)
```{r}
# There are 129971 wine tastings
(
  dat %>%
  count()
)

# There are 118840 wines
(
  dat %>%
    distinct(title) %>%
    summarize(
      n = n(),
    )
)

# These wines were tasted between 1 and 2 times
(dat %>%
  group_by(country, province, title) %>%
  summarize(
   n = n(),
  ) %>%
  arrange(desc(n))
)

# More wines were tasted in California
(dat %>% 
  group_by(country, province) %>%
  summarize(
   n = n(),
  ) %>%
  arrange(desc(n))
) 


```


Clean your data & deal with NA (note how / why you handle this)
```{r}
clean_dat = dat %>% 
  # # remove continuous values
  filter(
    !is.na(price), # from 129,971 to 120,975
  ) %>%
  # alter discrete values to "Unkown"
   mutate(
    region_1 = ifelse(is.na(region_1), "Unknown", region_1),
    region_2 = ifelse(is.na(region_2), "Unknown", region_2),
    taster_name = ifelse(is.na(taster_name), "Unknown", taster_name),
    taster_twitter_handle = ifelse(is.na(taster_twitter_handle), "Unknown", taster_twitter_handle),
    country = ifelse(is.na(country), "Unknown", country),
    province = ifelse(is.na(province), "Unknown", province)
  )
```


Explore the data via EDA methods from R4DS book
```{r}
View(clean_dat)
# Example
clean_dat %>%
  group_by(country) %>%
  ggplot(aes(x=country,y=price)) +
  geom_boxplot()
```



## Highlight anything interesting that you would want to look into below:
