---
title: "Assignment 04"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
```



Complete a hypothesis test on the `InsectSprays` data (`dat` below)

```{r}
data("InsectSprays")
dat = InsectSprays %>%
  rename(insects = count) %>%
  filter(spray == 'A' | spray == 'B')
dat
```

Begin your hypothesis test here. You can do it with both the analytical approach (`t.test`)  and the permutation test technique.

```{r}

```







## Explore the Data - Wine Data
Data from kaggle.com <https://www.kaggle.com/zynicide/wine-reviews>


#### Assignment  

If you were head of purchasing for a liquor store, what would you choose to buy and why?

```{r, message = FALSE, warning = FALSE}
dat = read_csv('https://foco-ds-portal-files.s3.amazonaws.com/winemag-data-130k-v2.csv')
head(dat)
```


Show summary statistics (note anything interesting)
```{r}
dat %>% 
```


Clean your data & deal with NA (note how / why you handle this)
```{r}
clean_dat = dat %>% 
```


Explore the data via EDA methods from R4DS book
```{r}
# Example
clean_dat %>%
  ggplot(aes()) %>% 
```



## Highlight anything interesting that you would want to look into below:
